---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# `spatial.extensions`

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/patter)](https://CRAN.R-project.org/package=patter)

`spatial.extensions` is `R` package that provides convenience functions for common spatial operations, extending `r-spatial` packages such as `terra` and `sf`. 

# Installation

The `spatial.extensions` package can be installed with: 

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("edwardlavender/spatial.extensions", 
                         dependencies = TRUE)
```

# Code of conduct

Please note that the `spatial.extensions` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
